\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-31 OaklandSubmission/security.tex

We shall assume a cryptographic \mpc backend that securely implements any circuit $\crct$ that is output by our compiler (see \figureref{circuits}). In more detail, this means that for any well-typed source program $s$, let $\crct$ be the circuit output by our compiler (as in \theoremref{correctness}). We assume that there exists a \mpc protocol $\prot$ that securely realizes the functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the corresponding simulator  (that runs on $\crct$, input of the corrupt party and the output obtained from trusted functionality for $\crct$). We note that the work of \cite{aby} provides such a protocol $\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$ output by our compiler. We are now ready to state and prove our security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be any functionality or program in our source language with outputs (or observations) $O_1$, that is compiled into a circuit $\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol $\prot$ be the two-party secure computation protocol that securely realizes $\chi$ (as defined above). Then, $\prot$ securely realizes $s$.  
\end{theorem}

>>>>

We shall assume a cryptographic \mpc backend that securely implements
any circuit $\crct$ that is output by our compiler
(see \figureref{circuits}). In more detail, this means that for any
well-typed source program $s$, let $\crct$ be the output circuit output
(as in \theoremref{correctness}). We assume that there
exists a \mpc protocol $\prot$ that securely realizes the
functionality $\crct$ and let $\simu_{\tiny{2pc}}$ be the
corresponding simulator  (that runs on $\crct$, input of the corrupt
party and the output obtained from trusted functionality for
$\crct$). We note that ABY~\cite{aby} provides such a protocol
$\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\crct$
output in our framework. We now state and prove our
security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be any functionality or program in our source language with
outputs (or observations) $O_1$, that outputs a circuit
$\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol
$\prot$ be the two-party secure computation protocol that securely
realizes $\chi$ (as defined above). Then, $\prot$ securely realizes
$s$.
\end{theorem}
